\documentclass[10pt,a4paper,sans]{moderncv}       

\moderncvstyle{casual}
\moderncvcolor{blue}      
\usepackage{changepage}     
\usepackage[bottom]{footmisc}                                         
% adjust the page margins
\usepackage[left=0.75 in,right= 0.75 in,top= 0.5 in,bottom= 1 in]{geometry}
\usepackage{ragged2e}
\setlength{\hintscolumnwidth}{2.4cm}                % if you want to change the width of the column with the dates
\usepackage[T1]{fontenc}
\usepackage{lmodern} 

\usepackage{totcount}

% Counter for Under Review Journal Articles
\newcounter{underReviewArticleCounterReverse}
\newtotcounter{underReviewArticleCounter}
\setcounter{underReviewArticleCounter}{1}

\newcommand{\underReviewArticle}[1]{%
	\addtocounter{underReviewArticleCounterReverse}{-1}
	\addtocounter{underReviewArticleCounter}{1}
	\cvitem{[\arabic{underReviewArticleCounterReverse}]}{%
		#1
	}
}

% Counter for Peer-Reviewed Journal Articles
\newcounter{peerReviewedArticleCounterReverse}
\newtotcounter{peerReviewedArticleCounter}
\setcounter{peerReviewedArticleCounter}{1}

\newcommand{\peerReviewedArticle}[1]{%
	\addtocounter{peerReviewedArticleCounterReverse}{-1}
	\addtocounter{peerReviewedArticleCounter}{1}
	\cvitem{[\arabic{peerReviewedArticleCounterReverse}]}{%
		#1
	}
}

% Counter for Peer-Reviewed Conference Articles
\newcounter{peerReviewedConferenceCounterReverse}
\newtotcounter{peerReviewedConferenceCounter}
\setcounter{peerReviewedConferenceCounter}{1}

\newcommand{\peerReviewedConference}[1]{%
	\addtocounter{peerReviewedConferenceCounterReverse}{-1}
	\addtocounter{peerReviewedConferenceCounter}{1}
	\cvitem{[\arabic{peerReviewedConferenceCounterReverse}]}{%
		#1
	}
}

% Counter for White Papers
\newcounter{whitePaperCounterReverse}
\newtotcounter{whitePaperCounter}
\setcounter{whitePaperCounter}{1}

\newcommand{\whitePaper}[1]{%
	\addtocounter{whitePaperCounterReverse}{-1}
	\addtocounter{whitePaperCounter}{1}
	\cvitem{[\arabic{whitePaperCounterReverse}]}{%
		#1
	}
}

% Counter for Pre-prints
\newcounter{preprintCounterReverse}
\newtotcounter{preprintCounter}
\setcounter{preprintCounter}{1}

\newcommand{\preprint}[1]{%
	\addtocounter{preprintCounterReverse}{-1}
	\addtocounter{preprintCounter}{1}
	\cvitem{[\arabic{preprintCounterReverse}]}{%
		#1
	}
}

% Counter for Research Summary Documents
\newcounter{ResearchSummaryCounterReverse}
\newtotcounter{ResearchSummaryCounter}
\setcounter{ResearchSummaryCounter}{1}

\newcommand{\researchSummary}[1]{%
	\addtocounter{ResearchSummaryCounterReverse}{-1}
	\addtocounter{ResearchSummaryCounter}{1}
	\cvitem{[\arabic{ResearchSummaryCounterReverse}]}{%
		#1
	}
}

% Counter for Presentations
\newcounter{presentationCounterReverse}
\newtotcounter{presentationCounter}
\setcounter{presentationCounter}{1}

\newcommand{\presentations}[1]{%
	\addtocounter{presentationCounterReverse}{-1}
	\addtocounter{presentationCounter}{1}
	\cvitem{[\arabic{presentationCounterReverse}]}{%
		#1
	}
}

% Counter for Invited Talks
\newcounter{invitedTalksCounterReverse}
\newtotcounter{invitedTalksCounter}
\setcounter{invitedTalksCounter}{1}

\newcommand{\invitedTalks}[1]{%
	\addtocounter{invitedTalksCounterReverse}{-1}
	\addtocounter{invitedTalksCounter}{1}
	\cvitem{[\arabic{invitedTalksCounterReverse}]}{%
		#1
	}
}
% Counter for Conference Session Organizations
\newcounter{sessionOrganizationCounterReverse}
\newtotcounter{sessionOrganizationCounter}
\setcounter{sessionOrganizationCounter}{1}

\newcommand{\sessionOrganization}[1]{%
	\addtocounter{sessionOrganizationCounterReverse}{-1}
	\addtocounter{sessionOrganizationCounter}{1}
	\cvitem{[\arabic{sessionOrganizationCounterReverse}]}{%
		#1
	}
}
% Counter for Local Session Organizations
\newcounter{localOrganizationCounterReverse}
\newtotcounter{localOrganizationCounter}
\setcounter{localOrganizationCounter}{1}

\newcommand{\localOrganization}[1]{%
	\addtocounter{localOrganizationCounterReverse}{-1}
	\addtocounter{localOrganizationCounter}{1}
	\cvitem{[\arabic{localOrganizationCounterReverse}]}{%
		#1
	}
}

% personal data
\name{Darryl}{Chamberlain Jr.}
\title{Curriculum Vitae}                              
%\address{600 S. Clyde Morris Blvd. Daytona Beach, FL 32114-3900}{}{}          
\email{Darryl.Chamberlain@erau.edu}    
\homepage{faculty.erau.edu/Darryl.Chamberlain}           

\raggedright  

\begin{document}
	\makecvtitle
	\vspace*{-1cm}
	\section{Education}
	\cventry{2023}
	{Certificate, Applied Data Science with Python}
	{}{}
	{\textit{University of Michigan (Coursera)}}
	{ Five-course specialization sequence in Applied Data Science. 
		\href{https://www.coursera.org/account/accomplishments/specialization/certificate/7TEVNZ89JDDA}{\underline{Credential URL}}  
	}
	{}
	\cventry{2012--2017}
	{Ph.D., Mathematics and Statistics}
	{}{}
	{\textit{Georgia State University}}
	{Qualifying Exams in Collegiate Mathematics Education, Abstract Algebra, and Matrix Analysis. \\ 
		\href{https://scholarworks.gsu.edu/math_diss/46/}{\underline{Dissertation}} qualitatively modeled how students develop an understanding of proof by contradiction. 
		%\\ Advised by Dr. Draga Vidakovic.
	}
	{}
	
	\cventry{2007--2010}
	{B.S., Mathematics}
	{University of Florida}
	{}{}{}
	\section{Professional Experience}
	\cventry{2021--present}
	{Assistant Professor}
	{}
	{Department of Mathematics, Science, and Technology}
	{Embry-Riddle Aeronautical University -- Worldwide}
	{}
	\cventry{2017--2021}
	{Assistant Instructional Professor}
	{}
	{Department of Mathematics}
	{University of Florida}
	{}
	\cventry{2013--2017}
	{Graduate Teaching Assistant}
	{}
	{Department of Mathematics and Statistics}
	{Georgia State University}
	{}
	\cventry{2011--2012}
	{Teacher}
	{}
	{Mathematics}
	{William T. Dwyer High School, Palm Beach County, FL}
	{} 
	\section{Administrative Experience}
	\cventry{2023--present}
	{Associate Chair}
	{}
	{Department of Mathematics, Science, and Technology}
	{Embry-Riddle Aeronautical University -- Worldwide}
	{}
	\cventry{Jan--May 2024}
	{Acting Chair}
	{}
	{Department of Mathematics, Science, and Technology}
	{Embry-Riddle Aeronautical University -- Worldwide}
	{}
	\cventry{2015--2016}
	{Emporium Lab Coordinator}
	{}
	{Department of Mathematics and Statistics}
	{Georgia State University}
	{}
	\section{External Research Funding Experience}
	\cventry{
		\$71,856\\ under review}
	{\textbf{Principal Investigator}}
	{Investigating the Development and Impact of Culturally Relevant, AI-Powered Pedagogies in Postsecondary Mathematics Education}
	{with Audrey Malagon (co-PI) and Gizem Karaali (co-PI). 
		Spencer Foundation Vision Grant, 2025-2026.}
	{}{}
	\cventry{
		\$398,725\\ under review}
	{\textbf{Principal Investigator}}
	{Collaborative Research: Adaptive Assessments in Calculus}
	{with Russell Jeter (Lead-PI) and Kelvin Rozier (co-PI). 
		NSF Improving Undergraduate STEM Education (IUSE), 2025-2029.}
	{}{}
	\cventry{
		\$26,962\\ unfunded}
	{\textbf{Co-Principal Investigator}}
	{EXCELing in STEM: The Impact of Empowering Student Engagement with the Public}
	{with Emily Faulconer (PI), Amy Gruss (supporting researcher), Effie Kartsonaki (supporting researcher), and Dong Jun Kim (supporting researcher). 
		Spencer Foundation Small Grants Program, 2025-2026.}
	{}{}
	\cventry{
		\$500\\ funded}
	{\textbf{Principal Investigator}}
	{Asycnchronous Discovery Activity - Learning to Fly with the Wind}
	{Doenet (DUE-1915294, DUE-1915363, DUE-1915438) Learning Experiment Mini-Grant, 2023-2024.}
	{}{}
	\cventry{
		\$399,183\\ funded}
	{\textbf{Co-Principal Investigator}}
	{Undergraduate Research for Fully Online STEM Students: Impact of Expanded Curricular Options on STEM Attitudes, Identity, \& Career Ambitions}
	{with Robert Deters (PI), Emily Faulconer (co-PI), Brent Terwilliger (co-PI). NSF Improving Undergraduate STEM Education (IUSE), 2023-2026.}
	{}{}
	\cventry{
		\$237,298\\ funded}
	{\textbf{Co-Principal Investigator}}
	{Community of Inquiry and Cognitive Load in Online STEM: Persistence, Performance, and Perspectives}
	{with Emily Faulconer (PI) and Beverly Wood (co-PI). NSF Improving Undergraduate STEM Education (IUSE), 2021-2024.}
	{}{}
	\cventry{
		\$271,543\\ unfunded}
	{\textbf{Principal Investigator}}
	{Drilling Down into Concepts with Automatic and Diagnostic Item Generation (Auto-DIG)}
	{with Annie Burns-Childers (co-PI), Catherine Paolucci (co-PI), and Russell Jeter (consult). NSF Improving Undergraduate STEM Education (IUSE), Submitted October 2020.}
	{}{}
	\cventry{
		\$202,184\\ unfunded}
	{\textbf{Co-Principal Investigator}}
	{Using Video to Expand Communication of Mathematical Sciences Research}
	{with Catherine Paolucci (PI). National Science Foundation, Submitted October 2020.}
	{}{}
	\cventry{
		\$99,960\\ unfunded}
	{\textbf{Principal Investigator}}
	{NSF ECR Core Research: Analyzing a Novel College Algebra Curriculum and Implementation}
	{with Russell Jeter (consult). NSF Directorate for STEM Education Core Research (ECR: Core), Submitted October 2019.}
	{}{}
	\cventry{
		\$340,764 \\ funded}
	{Graduate Research Assistant (2016--2017); Other Professional (2017--2021)}
	{Promoting Reasoning in Undergraduate Mathematics (PRIUM)}
	{with Draga Vidakovic (PI), Valerie Miller (Co-PI), and Guantao Chen (Co-PI). NSF Improving Undergraduate STEM Education (IUSE), 2016-2022.}
	{}{}
	
	\section{Internal Research Funding Experience}
	\cventry{
		\$26,000\\ under review}
	{Co-Principal Investigator}
	{Developing AI-Assisted Writing Technologies to Enhance College Writers’ Processes}
	{with Emily Dux Speltz (PI). 
		ERAU Faculty Innovative Research in Science and Technology (FIRST) Grant, 2025-2026.}
	{}{}
	\cventry{
		\$2,000\\ funded}
	{Co-Principal Investigator}
	{Generative AI Feedback Across the Disciplines: A College of Arts and Sciences Pilot Study}
	{with Alex Rister (PI), Anastasia Angelopoulou (co-PI), Cihan Aydiner (co-PI), Iuliia Hoben (co-PI), Logan Gerber-Chavez (co-PI), Zackery Reed (co-PI), and Meghan Velez (co-PI). 
		ERAU-WW COAS Start-Up Funding, 2024.}
	{}{}
	\cventry{
		\$6,000\\ funded}
	{Principal Investigator}
	{Collective Knowledge Progression and Proliferation in Asynchronous Calculus Discussion Boards}
	{with Zackery Reed (co-PI) and Karen Keene (co-PI). 
		ERAU-WW Faculty Seed Grant, 2023.}
	{}{}
	\cventry{
		\$4,069\\ funded}
	{Principal Investigator}
	{Developing Autonomous, Targeted Feedback in Precalculus}
	{ERAU-WW Faculty Seed Grant, 2021-2022.}
	{}{}
	\cventry{
		\$29,923\\ funded}
	{Co-Principal Investigator}
	{Examining and addressing the content knowledge development needs of Florida's aspiring and newly-qualified mathematics teachers}
	{with Catherine Paolucci (PI) and Christopher Redding (Co-PI). 
		UF Internal Grant, 2020-2021.}
	{}{}
	
	\section{Journal Articles Under Review}
	\setcounter{underReviewArticleCounterReverse}{\totvalue{underReviewArticleCounter}}
	%\underReviewArticle{%
		%	\textbf{Chamberlain Jr., D.}, Faulconer, E., \& Wood, B.
		%	(under review June 2024).
		%	\emph{Engaging Asynchronous Discussions: Impact of an Intervention to Enhance Community and Improve Learner Outcomes}. 
		%	Active Learning in Higher Education. \newline
		%     \textit{\underline{CRediT Roles:}} Data Curation, Formal Analysis, Methodology, Visualization, Writing - Original Draft.
		%}
	
	%\underReviewArticle{%
		%	\textbf{Chamberlain Jr., D.}, Faulconer, E., \& Wood, B.
		%	(under review June 2024).
		%	\emph{Direct Measures of Social, Cognitive, and Teacher Presence in Asynchronous, Online Discussions}. 
		%	International Journal of Educational Research.  \newline
		%   \textit{\underline{CRediT Roles:}} Data Curation, Formal Analysis, Methodology, Visualization, Writing - Original Draft.
		%}
	\underReviewArticle{%
		\textbf{Chamberlain Jr., D.}\footnotemark, Jeter, R.$^1$, \& Rozier, K. 
		(under review January 2025).
		\textit{Towards an Integrated Methodology for Assessing Item Discrimination in Mathematics Assessments}.
		Educational Assessment \newline 
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis,  Investigation, Methodology, Project Administration, Software, Visualization, Writing - Original Draft.
	}
	\footnotetext{Co-first authors.}
	\underReviewArticle{%
		Faulconer, E., Terwilliger, B., \textbf{Chamberlain Jr., D.}, Deters. R., \& Kam, C. (under review Oct 2024). 
		\textit{Virtual Mentorship for Online Undergraduate Research: Analysis of Mentors and Mentees' Perspectives}.
		Journal of Mentoring \& Tutoring. \newline
		\textit{\underline{CRediT Roles:}} Data Curation, Formal Analysis, Writing - Original Draft.
	}
	
	\section{Peer-Reviewed Journal Articles and Book Chapters}
	\setcounter{peerReviewedArticleCounterReverse}{\totvalue{peerReviewedArticleCounter}}
	\peerReviewedArticle{%
		\textbf{Chamberlain Jr., D.} \& Faulconer, E.
		(accepted Feb 2025).
		\emph{Structural Framework for Interactions Between Community of Inquiry Presences, Cognitive Load, Demographics, and Grades}.
		Active Learning in Higher Education. \newline
		\textit{\underline{CRediT Roles:}} Data Curation, Formal Analysis, Methodology, Visualization, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedArticle{%
		Velez, M., Reed, Z., \textbf{Chamberlain Jr., D.}, \& Aydiner, C. 
		(2025).
		\textit{Black Boxes Revisited: Understanding GenAI Responses to Students’ Written Work.}
		Thresholds in Education. \newline
		\textit{\underline{CRediT Roles:}} Data Curation, Formal Analysis, Methodology, Writing - Original Draft.
	}
	
	\peerReviewedArticle{%
		Reed, Z., \textbf{Chamberlain Jr., D.}, \& Ramirez, L.
		(2025).
		\emph{A Framework for Analyzing Asynchronous Discussion Activities.} 
		Teaching and Learning Mathematics Online 2e, CRC Press, FL.  \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Funding Acquisition, Investigation, Methodology, Project Administration, Software, Visualization, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedArticle{%
		Reid et al.
		(2024). 
		Voices from the field: How did you come to engage in students-as-partners work?
		\textit{International Journal for Students as Partners, 8(2)},
		241-259. 
		\href{https://doi.org/10.15173/ijsap.v8i2.5872}{https://doi.org/10.15173/ijsap.v8i2.5872}
		\newline
		\textit{\underline{CRediT Roles:}} Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedArticle{%
		\textbf{Chamberlain Jr., D.} 
		(2023).
		\emph{How one instructor can teach a large-scale, mastery-based College Algebra course online.} 
		Problems, Resources, and Issues in Mathematics Undergraduate Studies. DOI: 10.1080/10511970.2023.2190183.
	}
	\peerReviewedArticle{%
		Faulconer, E., \textbf{Chamberlain Jr., D.}, \& Wood, B. 
		(2022). 
		\textit{A Case Study of Community of Inquiry Presences and Cognitive Load in Asynchronous Online STEM Courses}.
		Online Learning Journal. DOI: http://dx.doi.org/10.24059/olj.v26i3.3386. \newline
		\textit{\underline{CRediT Roles:}} Data Curation, Formal Analysis, Methodology, Software, Visualization, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedArticle{%
		\textbf{Chamberlain Jr., D.} \& Vidakovic, D. 
		(2021).
		\emph{Cognitive trajectory of proof by contradiction for Transition-to-Proof students}.
		Journal of Mathematical Behavior.
		DOI: 10.1016/j.jmathb.2021.100849. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Investigation, Methodology, Project Administration, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedArticle{%
		\textbf{Chamberlain Jr., D.}$^1$ \& Jeter, R.$^1$
		(2020). 
		\emph{Creating diagnostic assessments: Automated distractor generation with integrity}. 
		Journal of Assessment in Higher Education. 
		DOI: 10.32473/jahe.v1i1.116892. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Funding Acquisition, Investigation, Methodology, Project Administration, Software, Visualization, Writing - Original Draft, Writing - Review \& Editing.
	}
	\footnotetext{Co-first authors.}
	\peerReviewedArticle{%
		\textbf{Chamberlain Jr., D.}, Grady, A., Keeran, S., Knudson, K., Manly, I., Shabazz, M., Stone, C., \& York, A. 
		(2020). 
		\textit{Transitioning to an active learning environment for calculus at the University of Florida.} 
		Problems, Resources, and Issues in Mathematics Undergraduate Studies.
		DOI: 10.1080/10511970.2020.1769235. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Methodology, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedArticle{
		Stalvey, H., Burns, A., \textbf{Chamberlain Jr., D.}, Kemp, A., Meadows, L., \& Vidakovic, D. 
		(2019). 
		\emph{Students' understanding of the concepts involved in hypothesis testing for one population.} 
		Journal of Mathematical Behavior. 
		DOI: 10.1016/j.jmathb.2018.03.011. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Investigation, Methodology, Writing - Original Draft, Writing - Review \& Editing.
	}
	
	\section{Peer-Reviewed Conference Proceedings {\footnotesize [asterisk denotes presenter]}}
	\setcounter{peerReviewedConferenceCounterReverse}{\totvalue{peerReviewedConferenceCounter}}
	
	\peerReviewedConference{
		Terwilliger, B.*, Deters. R., \& \textbf{Chamberlain Jr., D.}
		(2025, Jul 30).
		\textit{Exploring the Efficacy of Virtual Research Mentorship for Online Undergraduate Projects}.
		Distance Learning Administration (DLA) 2025 Annual Conference and Exposition, Jekyll Island, GA. \newline 
		\textit{\underline{CRediT Roles:}} Data Curation, Formal Analysis, Investigation, Methodology, Visualization, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedConference{
		Deters. R.*, Terwilliger, B., Faulconer, E., George, K., \& \textbf{Chamberlain Jr., D.}
		(2025, Jun 22-25).
		\textit{Impact of the COVID-19 Pandemic on Online Student Interest and Engagement in Undergraduate Research}.
		American Society for Engineering Education (ASEE) 2025 Annual Conference and Exposition, Montreal, Canada. \newline 
		\textit{\underline{CRediT Roles:}} Formal Analysis, Visualization, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedConference{
		\textbf{Chamberlain Jr., D.}
		(2025, Feb 27). 
		\textit{Choices You Make Should Matter: Asynchronous Discovery Activities}.
		Poster at the 27th Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, Alexandria, VA.
	}
	
	\peerReviewedConference{
		\textbf{Chamberlain Jr., D.}$^1$, Jeter, R.*$^1$, \& Rozier, K.
		(2025, Feb 27). 
		\textit{Distractor-Based Distractors: Adventures in Assessment Item Analysis}.
		Poster at the 27th Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, Alexandria, VA. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Investigation, Methodology, Project Administration, Software, Visualization, Writing - Original Draft, Writing - Review \& Editing.
	}
	
	\peerReviewedConference{
		\textbf{Chamberlain Jr., D.}*, McGuinness, P., Faulconer, E., \& Wood, B. (2024, Feb 22-24). 
		\textit{Using Trees to See a Forest: Leveraging Machine Learning to Classify Student Thinking.}
		Poster at 26th Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, Omaha, NE. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Investigation, Methodology, Writing - Original Draft, Writing - Review \& Editing.
	}
	
	\peerReviewedConference{
		\textbf{Chamberlain Jr., D.}*, Reed, Z.*, \& Keene, K.
		(2023, Feb 23-25). 
		\textit{Adapting the Argumentative Knowledge Construction Framework to Asynchronous Mathematical Discussions}.
		25th Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, Omaha, NE. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Funding Acquisition, Investigation, Methodology, Project Administration, Software, Visualization, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedConference{%
		Bailey, T.*, \textbf{Chamberlain Jr., D.}*, \& Christodoulopoulou, K.
		(2022, Feb 24-26). 
		\textit{Undergraduate's covariational reasoning across function representations}.
		24th Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, Boston, MA. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Funding Acquisition, Investigation, Methodology, Project Administration, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedConference{%
		Reed, Z.*, \textbf{Chamberlain Jr., D.*}, \& Keene, K.
		(2022, Feb 24-26).
		\textit{Argumentative knowledge construction in asynchronous calculus discussion boards}.
		Poster at 24th Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, Boston, MA. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Funding Acquisition, Investigation, Methodology, Visualization, Writing - Original Draft.
	}
	\peerReviewedConference{%
		Kemp, A.*, \textbf{Chamberlain Jr., D.}, Cooley, L., Miller, V., \& Vidakovic, D. 
		(2020, Feb 27-29). 
		\textit{Student self- and simulated peer-evaluation of proof comprehension: Tina}. 
		23rd Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, Boston, MA. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Investigation, Methodology, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedConference{%
		\textbf{Chamberlain Jr., D.*} \& Jeter, R. 
		(2019, Feb 28-Mar 2). 
		\textit{Leveraging cognitive theory to create large-scale learning tools}.
		22nd Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, Oklahoma City, OK. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Funding Acquisition, Investigation, Methodology, Project Administration, Software, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedConference{%
		\textbf{Chamberlain Jr., D.*} \& Vidakovic, D. 
		(2018, Feb 22-24). 
		\emph{Developing proof comprehension and proof by contradiction through logical outlines}. 
		21st Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, San Diego, CA. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Investigation, Methodology, Project Administration, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedConference{%
		Burns, A.*, \textbf{Chamberlain Jr., D.}, Kemp, A.*, Meadows, L., Stalvey, H., \& Vidakovic, D. 
		(2018, Feb 22-24). 
		\emph{Reasoning about one population hypothesis testing: The case of Steve}. 
		21st Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, San Diego, CA. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Investigation, Methodology, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedConference{%
		\textbf{Chamberlain Jr., D.*} \& Vidakovic, D. 
		(2017, Feb 23-25). 
		\emph{Developing student understanding: The case of proof by contradiction}. 
		20th Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, San Diego, CA. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Investigation, Methodology, Project Administration, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedConference{%
		Burns, A.*, \textbf{Chamberlain Jr., D.}, Kemp, A.*, Meadows, L., Stalvey, H., \& Vidakovic, D. 
		(2017, Feb 23-25). 
		\emph{Students' understanding of test statistics in hypothesis testing}. 
		20th Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, San Diego, CA. \newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Investigation, Methodology, Writing - Original Draft, Writing - Review \& Editing.
	}
	\peerReviewedConference{%
		Abel, T.*, Brazas, J.*, \textbf{Chamberlain Jr., D.}, \& Kemp, A. 
		(2017, Feb 23-25). 
		\emph{Characterizing mathematical digital literacy: A preliminary investigation}. 
		20th Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, San Diego, CA. \newline
		\textit{\underline{CRediT Roles:}} Data Curation, Formal Analysis, Investigation, Writing - Original Draft, Writing - Review \& Editing.
	}	
	\peerReviewedConference{%
		\textbf{Chamberlain Jr., D.*} \& Vidakovic, D. 
		(2016, Feb 25). 
		\emph{Use of strategic knowledge in a transition-to-proof course: Differences between an undergraduate and graduate student}. 
		19th Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME, Pittsburgh, PA. %Retrived from \href{http://sigmaa.maa.org/rume/crume2016/Papers/RUME\_19\_paper\_7.pdf}{http://sigmaa.maa.org/rume/crume2016/Papers/RUME\_19\_paper\_7.pdf}
		\newline
		\textit{\underline{CRediT Roles:}} Conceptualization, Data Curation, Formal Analysis, Investigation, Methodology, Project Administration, Writing - Original Draft, Writing - Review \& Editing.
	}
	\section{White Papers}
	\setcounter{whitePaperCounterReverse}{\totvalue{whitePaperCounter}}
	
	\whitePaper{%
		Faulconer, E., \textbf{Chamberlain Jr., D.}, \& Wood, B. (2024). \textit{Community of Inquiry and Cognitive Load: Research Summary Document.} Zenodo. \href{https://zenodo.org/doi/10.5281/zenodo.7951445}{https://doi.org/10.5281/zenodo.11398144}
	}
	\whitePaper{%
		Faulconer, E., \textbf{Chamberlain Jr., D.}, \& Wood, B.
		(2024).
		\textit{Community of Inquiry and Cognitive Load in online STEM: Transferability plan}.
		Zenodo. DOI: \href{https://doi.org/10.5281/zenodo.11203344}{https://doi.org/10.5281/zenodo.11203344}
		\newline
		\textit{\underline{CRediT Roles:}} Data Analysis, Writing - Review \& Editing.
	}
	
	\whitePaper{%
		Wood, B., Faulconer, E., \& \textbf{Chamberlain Jr., D.},
		(2024).
		\textit{Gathering Nuanced Data for Understanding Student Withdrawals}.
		Zenodo. DOI: \href{https://doi.org/10.5281/zenodo.11094757}{10.5281/zenodo.11094757}
		\newline
		\textit{\underline{CRediT Roles:}} Writing - Review \& Editing.
	}
	\section{Pre-Prints}
	\setcounter{preprintCounterReverse}{\totvalue{preprintCounter}}
	
	\preprint{%
		\textbf{Chamberlain Jr., D.}$^1$, Jeter, R.$^1$, \& Rozier, K. 
		(2024, December 27).
		\textit{An Integrated Methodology for Assessing Item Discrimination in Mathematics Assessments}.
		https://doi.org/10.31235/osf.io/xvh7y
	}
	\footnotetext{Co-first authors.}
	\preprint{%
		\textbf{Chamberlain Jr., D.}, \& Jeter, R. 
		(2024, August 9). 
		\textit{Utilizing Theoretically-Driven Distractors to Make Diagnostic Multiple-Choice Assessments Possible}. 
		https://doi.org/10.31235/osf.io/vzhm7
	}
	
	\preprint{%
		\textbf{Chamberlain Jr., D.}, \& Faulconer, E. 
		(2024, July 3). 
		\textit{Structural Framework for Interactions Between Community of Inquiry Presences, Cognitive Load, Demographics, and Grades. }
		https://doi.org/10.31235/osf.io/7ay4t
	}
	
	%\section{Research Summary Documents}
	%\setcounter{researchSummaryCounterReverse}{\totvalue{researchSummaryCounter}}
	%\researchSummary{%
		%	Faulconer, E., \textbf{Chamberlain Jr., D.}, \& Wood, B. (2024). \textit{Community of Inquiry and Cognitive Load: Research Summary Document.} Zenodo. \href{https://zenodo.org/doi/10.5281/zenodo.7951445}{https://doi.org/10.5281/zenodo.11398144}
		%}
	
	\section{Conference Presentations {\footnotesize [asterisk denotes presenter]}}
	\setcounter{presentationCounterReverse}{\totvalue{presentationCounter}}
	
	\presentations{
		\textbf{Chamberlain Jr., D.}*, Jeter, R., \& Rozier, K.
		(2025, Apr 15-16)
		\textit{Who Assesses the Assessments? Methodology for Classifying Assessment Items}.
		2025 Division of Academic Innovation (DAI) Virtual Conference (virtual).
	}
	\presentations{
		\textbf{Chamberlain Jr., D.}* \& Nowell, J.
		(2025, Feb 19).
		\textit{Longitudinal Impacts Analysis of Course Designs on Future Course Success}.
		Intersections: Online Learning and Innovation in Higher Education, Orlando, FL. 
	}
	\presentations{
		Reed, Z. \& \textbf{Chamberlain Jr., D.} 
		(2025, Feb 14).
		\textit{Promoting Argumentation and Discourse in Mathematics Courses}.
		3rd Annual Humanistic STEM Symposium, Daytona Beach, FL (virtual).
	}
	\presentations{
		\textbf{Chamberlain Jr., D.}*, Faulconer, E., Terwilliger, B., \& Deters. R.
		(2024, Nov 7).
		\textit{Cultivating Cyber Scholars: Research Support for Online STEM Students}.
		American Association of Colleges and Universities (AAC\&U) 2024 Transforming STEM Higher Education Conference, Arlington, VA.
	}
	\presentations{
		Faulconer, E., Terwilliger, B.*, Deters. R., \&  \textbf{Chamberlain Jr., D.}
		(2024, Jul 30).
		\textit{Supporting Undergraduate Research for Fully Online Students}.
		Distance Learning Administration Conference, Jekyll Island, GA.
	}
	\presentations{
		Velez, M.*, \textbf{Chamberlain Jr., D.}, \& Hoben, I.
		(2024, Jul 22-24).
		\textit{Beyond Text Generation: Incorporating GenAI Feedback in Asynchronous Online Courses}.
		2nd Annual Teaching and Learning with AI Conference, Orlando, FL.
	}
	\presentations{
		\textbf{Chamberlain Jr., D.}* \& Quinlan, J.
		(2023, Aug 2). 
		\textit{Technology Use in Undergraduate Mathematics Classrooms}.
		2023 Mathematical Association of America MathFest, Tampa, FL. 
	}
	\presentations{
		\textbf{Chamberlain Jr., D.}*, Reed, Z.*, Rister, A.*, \& Velez, M.*
		(2023, Feb 7). 
		Roundtable discussion: \textit{Practical Suggestions to Improve Online Discussions Across Disciplines}.
		2023 Division of Academic Innovation (DAI) Virtual Conference (virtual).
	}
	\presentations{
		Faulconer, E.*, \textbf{Chamberlain Jr., D.*}, \& Wood, B.
		(2022, April 13). 
		\textit{Instructional Efficiency in Asynchronous Online Discussions}.
		Online Learning Consortium Innovate Conference, Dallas, TX.
	}
	\presentations{%
		Paolucci, C.*, \textbf{Chamberlain Jr., D.}, \& Vancini, S.*
		(2022, Apr 7).
		\textit{Investigating alternatively-certified teachers' mathematical knowledge for teaching calculus}.
		Joint Mathematics Meeting, Seattle, WA.
	}
	\presentations{%
		\textbf{Chamberlain Jr., D.*}, Reed, Z., \& Keene, K.
		(2021, Nov 20).
		\textit{Investigating social construction of knowledge during asynchronous discussions}.
		5th Northeastern Conference on Research in Undergraduate Mathematics Education. New Brunswick, NJ (virtual).
	}
	\presentations{%
		Babiceanu, L.* \& \textbf{Chamberlain Jr., D.}
		(2021, Feb 20).
		\textit{Analyzing student achievement with residential and online students in College Algebra}.
		Florida Section of the Mathematical Association of America and Florida Two-Year College Mathematics Association 2021 Joint Meeting, Gainesville, FL (virtual).
	}
	\presentations{%
		\textbf{Chamberlain Jr., D.*} \& Jeter, R.
		(2021, Jan 7).
		\textit{Automated AF: Leveraging augmented intelligence to provide automated, actionable feedback.}
		Joint Mathematics Meeting, Washington, D.C. (virtual).
	}
	\presentations{%
		\textbf{Chamberlain Jr., D.*}  \& Jeter, R.
		(2020, Oct 20). 
		\textit{Incorporating Augmented Intelligence to Enhance Learning: Automatic and Diagnostic Item Generation (Auto-DIG)}. 
		STEMpowered Faculty Symposium, Gainesville, FL (virtual).
	} 
	\presentations{%
		\textbf{Chamberlain Jr., D.*} \& Vidakovic, D.
		(2020, Oct 3).
		\textit{Potential cognitive obstacles to understanding proof by contradiction.}
		4th Northeastern Conference on Research in Undergraduate Mathematics Education. Philadelphia, PA (virtual).
	}
	\presentations{%
		\textbf{Chamberlain Jr., D.*} 
		(2020, Jul 30). 
		\textit{Drilling down into content with Auto-DIG: Automatic Diagnostic Item Generation.} 
		MAA MathFest, Philadelphia, PA.
		\textit{Session canceled due to COVID-19 pandemic.}
	}
	\presentations{%
		\textbf{Chamberlain Jr., D.*} 
		(2020, Jan 18). 
		\textit{Mastery-based assessment in a large-enrollment online College Algebra course.}
		Joint Mathematics Meeting, Denver, CO.
	}
	\presentations{%
		\textbf{Chamberlain Jr., D.}, Knudson, K., Grady, A.*, Keeran, S., Manly, I., Shabazz, M., Stone, C., \& York, A. 
		(2020, Jan 18). 
		\textit{Active Calculus at the University of Florida.} 
		Joint Mathematics Meeting, Denver, CO.
	}
	\presentations{%
		\textbf{Chamberlain Jr., D.*} \& Jeter, R. 
		(2019, Apr 5). 
		\textit{Creating diagnostic assessments: Automated distractor generation with integrity}. 
		2019 Assessment in Higher Education: Enhancing Institutional Excellence, Gainesville, FL.
	}
	\presentations{%
		Jeter, R.* \& \textbf{Chamberlain Jr., D.} 
		(2018, Mar 24). 
		\emph{A novel method for creating assessment and diagnostic tools in the classroom}.
		MAA Southeastern Spring Sectional Meeting, Clemson, SC.
	}	
	\presentations{%
		\textbf{Chamberlain Jr., D.*} \& Vidakovic, D. 
		(2017, Mar 11). 
		\emph{Active learning in transition-to-proof courses: An example lesson of proof by contradiction}. 
		AMS Southeastern Spring Sectional Meeting, Charleston, SC.
	}
	\presentations{%
		\textbf{Chamberlain Jr., D.*} \& Vidakovic, D. 
		(2017, Jan 5). 
		\emph{A first lesson on proof by contradiction: Developing proof comprehension in a transition-to-proof course}. 
		Joint Mathematics Meeting, Atlanta, GA.
	}	
	\presentations{%
		\textbf{Chamberlain Jr., D.*}, Kemp, A.*, Meadows, L.*, Stalvey, H., Vidakovic, D., \& Burns, A. 
		(2016, Mar 5). 
		\emph{The emporium model for elementary statistics: A preliminary report}. 
		AMS Southeastern Spring Sectional Meeting, Athens, GA.
	}	
	\presentations{%
		\textbf{Chamberlain Jr., D.*} \& Vidakovic, D. 
		(2015, Apr 17). 
		\emph{APOS Theory in the classroom}. 
		Center for Instructional Effectiveness Annual Conference, Atlanta, GA.
	}	
	\presentations{%
		\textbf{Chamberlain Jr., D.*}, Vidakovic, D., Stalvey, H., Burns, A., Meadows, L., \& Kemp, A.* 
		(2015, Apr 10). 
		\emph{Student understanding of one population hypothesis testing: A piece of the process}. 
		Mathematics Graduate Student Miniconference, Atlanta, GA.
	}	
	\presentations{%
		\textbf{Chamberlain Jr., D.}* \& Vidakovic, D. 
		(2015, Apr 10). 
		\emph{Teaching proofs with APOS Theory}. 
		Mathematics Graduate Student Miniconference, Atlanta, Ga.
	}
	
	\section{Conference Session or Workshop Organization}
	\setcounter{sessionOrganizationCounterReverse}{\totvalue{sessionOrganizationCounter}}
	
	\sessionOrganization{
		\textbf{Chamberlain Jr., D.}, Reed, Z., \& Margolis, C. (2025, Feb 27). Workshop: \textit{Research on Technology in Undergraduate Mathematics Education}. 27th Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME,
		Alexandria, VA. 
	}
	\sessionOrganization{
		\textbf{Chamberlain Jr., D.} \& Reed, Z. (2024, Feb 22). Workshop: \textit{Research on Technology in Undergraduate Mathematics Education}. 26th Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME,
		Omaha, NE. 
	}
	\sessionOrganization{
		\textbf{Chamberlain Jr., D.} \& Barber, R. (2023, Aug 2). Session: \textit{Unspoken Research Components}. 
		2023 MAA MathFest, 
		Tampa, FL.
	}
	\sessionOrganization{
		\textbf{Chamberlain Jr., D.} \& Barber, R. (2023, Aug 2). Session: \textit{Building a Research Program}. 
		2023 MAA MathFest, 
		Tampa, FL.
	}
	\sessionOrganization{
		\textbf{Chamberlain Jr., D.}, Reed, Z., \& Keene, K. (2023, Feb 23). Workshop: \textit{Research on Technology in Undergraduate Mathematics Education}. 25th Annual Conference on Research in Undergraduate Mathematics Education: SIGMAA on RUME,
		Omaha, NE. 
	}
	\sessionOrganization{
		\textbf{Chamberlain Jr., D.}, Acu, B., \& Gasiorek, S. (2023, Jan 3). Session: \textit{Navigating the Early Years of the Faculty Experience}. 
		2023 Joint Mathematics Meeting, 
		Boston, MA.
	}
	\sessionOrganization{%
		Vidakovic, D., Stalvey, H., \textbf{Chamberlain Jr., D.}, Kemp, A., Meadows, L., \& Kellam, A. (2018, Mar 23-24).
		Session: \textit{Active Learning in Undergraduate Mathematics}. 
		MAA Spring 2018 Southeastern Section Conference, 
		Clemson, SC.
	}
	\sessionOrganization{%
		Vidakovic, D., Stalvey, H., \textbf{Chamberlain Jr., D.}, Kemp, A., \& Meadows, L. (2017, Mar 10-12).
		Session: \textit{Active Learning in Undergraduate Mathematics}. 
		AMS Spring 2017 Southeastern Regional Conference, 
		Charleston, SC.
	}
	\sessionOrganization{%
		Vidakovic, D., Stalvey, H., \textbf{Chamberlain Jr., D.}, Kemp, A., \& Meadows, L. (2016, Mar 5-6). 
		Session: \textit{Active Learning in Undergraduate Mathematics}. 
		AMS Spring 2016 Southeastern Regional Conference, 
		Athens, GA.
	}
	
	\section{Invited Talks}
	\setcounter{invitedTalksCounterReverse}{\totvalue{invitedTalksCounter}}
	
	\invitedTalks{%
		\textbf{Chamberlain Jr., D.}
		(2025, Apr 11).
		\textit{Modeling Student Thinking to Improve Mathematics Assessments}.
		Invited by Georgia State University Department of Mathematics and Statistics Seminar Series.
	}
	\invitedTalks{%
		\textbf{Chamberlain Jr., D.}
		(2024, Mar 21).
		\textit{Constructing Isn't Enough: Considering All Aspects of Proof}.
		Invited by University of Florida College of Education Special Topics Seminar Course.
	}
	\invitedTalks{%
		\textbf{Chamberlain Jr., D.}
		(2024, Mar 18).
		\textit{What Your Course Design Says About You: How Epistemological Lens Can Drive Course Design}.
		Invited by University of Florida Mathematics Department Pedagogy Seminar Series.
	}
	\invitedTalks{%
		\textbf{Chamberlain Jr., D.}
		(2023, Mar 29).
		\textit{Predicting Students' Thoughts to Provide Elaborative Feedback}.
		Invited by California State University Bakersfield Mathematics Department Seminar Series.
	}
	\invitedTalks{%
		Faulconer, E., Bourdeau, D., Kiernan, K., \& \textbf{Chamberlain Jr., D.}
		(2023, Jan 21).
		\textit{Non-Traditional Scholarly Publication}. 
		Invited by Embry-Riddle Aeronautical University -- Worldwide Research Scholars Program.
	}
	\invitedTalks{%
		\textbf{Chamberlain Jr., D.} \& Faulconer, E.
		(2022, Apr 21).
		\textit{How We Manage Large-Scale Data Collection}. 
		Invited by Embry-Riddle Aeronautical University -- Worldwide College of Arts and Sciences Brown Bag Lunch \& Learn Series.
	}
	\invitedTalks{%
		Paolucci, C. \& \textbf{Chamberlain Jr., D.}
		(2021, Mar 25).
		\textit{A profile of the content knowledge development needs of Florida's alternatively-certified teachers}. 
		Invited by University of Florida Education Policy Research Center Research Brown Bag Series.
	}
	\invitedTalks{%
		\textbf{Chamberlain Jr., D.} 
		(2020, Nov 13).
		\textit{Integrating Augmented Intelligence into Mathematics Education}. 
		Invited by Florida International University Mathematics Education Seminar.
	}
	\invitedTalks{%
		\textbf{Chamberlain Jr., D.} 
		(2020, Sept 17).
		\textit{Automatic and Diagnostic Item Generation}. 
		Invited by the University of Florida Lastinger Center.
	}
	\section{Local Session or Workshop Organization}
	\setcounter{localOrganizationCounterReverse}{\totvalue{localOrganizationCounter}}
	
	\localOrganization{%
		\textbf{Chamberlain Jr., D.}, Deters, R., \& Terwilliger, B. 
		(2025, March). 
		\textit{Open Data \& Data Papers}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	\localOrganization{%
		\textbf{Chamberlain Jr., D.}, Deters, R., \& Terwilliger, B. 
		(2025, February). 
		\textit{Identifying Research Gaps \& Developing Original Ideas}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	\localOrganization{%
		Terwilliger, B., Deters, R., \& \textbf{Chamberlain Jr., D.} 
		(2025, January). 
		\textit{Research Networking in the Online World}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	\localOrganization{%
		\textbf{Chamberlain Jr., D.}, Deters, R., Terwilliger, B., \& Faulconer, E., 
		(2024, October). 
		\textit{Staying Current on Research Advancements in Your Field}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	\localOrganization{%
		Deters, R., Terwilliger, B., \textbf{Chamberlain Jr., D.}, \& Faulconer, E.
		(2024, September). 
		\textit{Navigating Common Student Research Challenges}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	\localOrganization{%
		Deters, R., Terwilliger, B., \textbf{Chamberlain Jr., D.}, \& Faulconer, E.,
		(2024, August). 
		\textit{How to Use the WW-RSP Canvas Site \& Other Resources}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	\localOrganization{%
		Deters, R., Faulconer, E., Terwilliger, B., \& \textbf{Chamberlain Jr., D.},
		(2024, June). 
		\textit{Mentoring: A Guided Expedition Through Research Pathways}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	\localOrganization{%
		Faulconer, E., Deters, R., Terwilliger, B., \& \textbf{Chamberlain Jr., D.},
		(2024, May). 
		\textit{Submitting to Beyond}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	\localOrganization{%
		Terwilliger, B., Deters, R., Faulconer, E., \& \textbf{Chamberlain Jr., D.},
		(2024, April). 
		\textit{Innovative Dissemination}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	\localOrganization{%
		Terwilliger, B., Deters, R., Faulconer, E., \& \textbf{Chamberlain Jr., D.},
		(2024, March). 
		\textit{Marketing Your Research Experience}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	\localOrganization{%
		Faulconer, E., Deters, R., Terwilliger, B., \& \textbf{Chamberlain Jr., D.},
		(2024, February). 
		\textit{Discovery Day 2024}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	\localOrganization{%
		Deters, R., Terwilliger, B., Faulconer, E., \& \textbf{Chamberlain Jr., D.},
		(2024, January). 
		\textit{Funding Your Research}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	\localOrganization{%
		\textbf{Chamberlain Jr., D.}, Faulconer, E., Terwilliger, B., \& Deters, R.,
		(2023, November). 
		\textit{Current Research Opportunities}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	\localOrganization{%
		Faulconer, E., Terwilliger, B., Deters, R., \& \textbf{Chamberlain Jr., D.},
		(2023, October). 
		\textit{Meet the Mentors}. 
		ERAU Worldwide Research Scholars Workshop Series. 
	}
	
	\section{Teaching Experience} 
	\cventry{2024--present}
	{Boundary Value Problems}
	{Developer/Instructor}{}{}
	{\begin{itemize}
			\item Asynchronous online with $15-20$ students.
	\end{itemize} }
	\cventry{2023--present}
	{Introduction to Programming for Data Science}
	{Developer/Instructor}{}{}
	{\begin{itemize}
			\item Asynchronous online with $10-20$ students.
	\end{itemize} }
	\cventry{2021--present}
	{Precalculus for Aviation}
	{Developer/Instructor}{}{}
	{\begin{itemize}
			\item Asynchronous online with $20-30$ students.
			\item October 2022: EagleVision with 20 students.
	\end{itemize} }
	\cventry{2021--present}
	{Precalculus Essentials}
	{Instructor}{}{}
	{\begin{itemize}
			\item Asynchronous online with $20-30$ students.
	\end{itemize} }
	\cventry{2018--2021}{Analytic Geometry and Calculus I}{Instructor}{}{}{\begin{itemize}
			\item Fall 2019, Fall 2020: Special flipped class for $\sim$15 Pre-Health PostBac students. 
			\item Summer 2018: Special flipped classroom with $\sim$20 freshmen engineering students.
			\item Spring 2018: Large lecture with 200+ students.
	\end{itemize}}
	\cventry{Spring 2021}{Sets and Logic}{Developer/Instructor}{}{}{\begin{itemize}
			\item Modified Moore's Method with $\sim$30 students. \end{itemize}}
	\cventry{Summer 2019}{Analytic Geometry and Calculus II}{Instructor}{}{}{\begin{itemize}
			\item Flipped class with $\sim$20 students. \end{itemize}}
	\cventry{Spring 2019}{Elementary Differential Equations}{Instructor}{}{}{\begin{itemize}
			\item Large lecture with 120+ students.
	\end{itemize}}
	\cventry{2017--2021}
	{College Algebra}
	{Developer/Coordinator/Instructor}{}{}
	{\begin{itemize}
			\item Multiple sections of Pure Online ($\sim$150 students) and Hyrbid ($\sim$200 students) per semester. 
			\item Curriculum overhaul with focus on understanding of functions.
			\item Developed open-source online homework system/textbook with dynamically-generated problems.
			\item Developed automatically-generated assessments based on students' varying levels of understanding functions.
	\end{itemize}}
	\cventry{2013--2017}{Various courses}{Instructor of Record as graduate student}{}{}{\begin{itemize}
			\item Elementary Statistics (flipped, $\sim$40 student sections).
			\item Intermediate Algebra (traditional, $\sim$20 student section).
			\item College Algebra (flipped, $\sim$40 student sections).
			\item Support for College Algebra (co-req course, flipped, $\sim$40 student sections).
			\item Precalculus (flipped, $\sim$40 student sections).
	\end{itemize}}
	
	\section{Mentoring}
	\cvitem{2024--present}{
		\textbf{Graduate Research}
	}
	\cvitem{2020--present}{
		\textbf{Undergraduate Research}
		%	\begin{itemize}
			%		\item Teegan Bailey -- Covariational Reasoning
			%			\begin{itemize}
				%				\item 2020 UF Emerging Scholar
				%			\end{itemize}
			%		\item Laura Babiceanu -- Measurement Theory
			%	\end{itemize}
	}
	
	%\vspace*{-4mm}
	
	\cvitem{2019--2020}{
		\textbf{Masters of Arts in Teaching Mathematics} %- Ashley Watts
	}
	\cvitem{2019--2021}{
		\textbf{3\textsuperscript{rd}$\backslash$4\textsuperscript{th} year First Generation Student Life Coach}
		%	\begin{itemize}
			%		\item Ariel Gholar (2020--2021)
			%		\item Haley Hodes (2020--2021)
			%		\item Javier Moreno (2019--2020)
			%	\end{itemize}
	}
	
	%\vspace*{-4mm}
	
	\cvitem{2018--2021}{
		\textbf{University Minority Mentor Program}
		%	\begin{itemize}
			%		\item Anikka Bingcang (2019--2020)
			%		\item Yukai He (2019--2020)
			%		\item Angelica Morales (2018--2019)
			%	\end{itemize}
	}
	%\vspace*{-4mm}
	
	\section{Professional Leadership}
	\cvitem{
		2022--present}
	{\textbf{Council Member} for Mathematical Association of America Council on Teaching and Learning.}
	\cvitem{
		2022--present}
	{\textbf{Subcommittee Chair} for Mathematical Association of America Subcommittee on Technology in Mathematics Education (STME). Member since 2021.}
	
	\cvitem{
		2022}
	{\textbf{Nominating Committee Member} for the Research in Undergraduate Mathematics Education (RUME) community.}	
	\cvitem{
		2020--2022}
	{\textbf{Program Committee Member} for Research in Undergraduate Mathematics Education (RUME) annual conferences.}
	\cvitem{2018--2019}{
		\textbf{Huddle Leader} for the \textit{Florida College System} year-long Florida Mathematics Re-Design workgroups.
	}
	
	\section{Professional Service}
	\cvitem{2022--present}{
		\textbf{Grant Reviewer} for the National Science Foundation.
	}
	\cvitem{2017--present}{
		\textbf{Journal Reviewer} for
		\begin{itemize}
			\item \textit{International Journal of Innovative Science and Modern Engineering} since 2024;
			\item \textit{Educational Studies in Mathematics} since 2022;
			%\item \textit{Cogent Education} since 2021;
			\item \textit{Mathematical Thinking and Learning} since 2021;
			%\item \textit{Educational Research and Review} since 2021;
			\item \textit{International Journal of Research in Mathematics Education} since 2020;
			%\item \textit{Assessment \& Evaluation in Higher Education} since 2020;
			\item \textit{Journal of Assessment in Higher Education} since 2019;
			\item \textit{Journal of Mathematical Behavior} since 2017; and
			\item \textit{Problems, Resources, and Issues in Mathematics Undergraduate Studies} since 2017.
		\end{itemize}
	}
	
	\cvitem{2017}{
		\textbf{Poster judge} for 
		\textit{Joint Mathematics Meeting, Atlanta, GA}.
	}
	
	\cvitem{2016--present}{
		\textbf{Conference Reviewer} for 
		\textit{Annual Conference on Research in Undergraduate Mathematics Education}.
	}
	
	\section{University Service}
	\cvitem{2024-2025}{
		\textbf{Committee Member} for ERAU-WW End-of-Course Faculty Survey committee. 
	}
	\cvitem{2024}{
		\textbf{Hiring Committee Member} for Director of IT Service Management \& Worldwide IT Services.
	}
	\cvitem{2023--present}{
		\textbf{Educational Experiences Member} for the ERAU-WW Quality Enhancement Plan committee. 
	}
	\cvitem{2023--present}{
		\textbf{Grant Reviewer} for ERAU Faculty Innovative Research in Science and Technology (FIRST) grant. 
	}
	\cvitem{2022--2023}{
		\textbf{Grant Reviewer} for ERAU-WW Faculty SEED grant. 
	}
	\cvitem{2022--2025}{
		\textbf{Academic Technology Committee Chair} for ERAU-WW Faculty Senate. 
	}
	\section{College Service}
	%\cvitem{2023}{
		%	\textbf{Appeal Committee Member} for ERAU College of Arts and Sciences.
		%}
	\cvitem{2024}{
		\textbf{Hiring Committee Member} for tenured Department Chair search for Department of Behavioral and Social Science.
	}
	\cvitem{2022--2023}{
		\textbf{Faculty Council Member} for ERAU-WW College of Arts and Sciences.
	}
	\cvitem{2020--2021}{
		\textbf{Steering Committee Member} for the University of Florida College of Liberal Arts and Sciences.
	}
	\cvitem{2019--2021}{
		\textbf{Curriculum Committee Chair} for the University of Florida College of Liberal Arts and Sciences. \textit{Member 2019--2020.}
	}
	\cvitem{2018}{
		\textbf{Commencement Marshal}
		on behalf of the College of Liberal Arts and Sciences for the University of Florida's Spring 2018 and Summer 2018 undergraduate commencement ceremonies.
	}
	
	\section{Departmental Service}
	\cvitem{2024--present}{
		\textbf{Committee Member} for Department of Mathematics, Science, and Technology standing committees:
		\begin{itemize}
			\item \textbf{Chair}, Curriculum; 
			\item \textbf{Member}, Operations; and
			\item \textbf{Member}, Research \& Promotion.
		\end{itemize}
	}
	
	\cvitem{2022--present}{
		\textbf{Program Coordinator} for Department of Mathematics, Science, and Technology programs:
		\begin{itemize}
			\item Bachelor's Degree in Data Science (2025-present); 
			\item Minor in Applied Data Science (2022-present);
			\item Minor in Applied Mathematics (2022-2023);
		\end{itemize}
	} 
	
	\cvitem{2021--present}{
		\textbf{ERAU-WW Hiring Committee Participant}:
		\begin{itemize}
			\item \textbf{Chair}, Tenure-track candidate in Physical Science (2024-2025); 
			\item \textbf{Member}, Tenured Department Chair (2024);
			\item \textbf{Member}, Tenure-track candidate in Data Science (2022-2023)
		\end{itemize}
	} 
	
	\cvitem{2021--present}{
		\textbf{Course Mentor} for Department of Mathematics, Science, and Technology
		\begin{itemize}
			\item \textbf{Current}
			\begin{itemize}
				\item DSCI 411 - Applied Data Science Capstone (since 2025)
				\item DSCI 201 - Intro to Data Science (since 2024)
				\item CSCI 251 - Intro to Programming for Data Science (since 2023)
				\item MATH 112 - Applied Calculus for Aviation (since 2023)
				\item MATH 111 - Pre-Calculus for Aviation (since 2022)
				\item STAT 412 - Probability \& Statistics (since 2022)
				\item MATH 502 - Boundary Value Problems (since 2021)
			\end{itemize}
			\item \textbf{Past}
			\begin{itemize}
				\item MATH 546 - Application-Based Advanced Engineering Mathematics (2021--2024)
				\item GNED 103 - Basic Mathematics (2021--2022)
				\item MATH 106 - Basic Algebra \& Trigonometry (2021--2022)
			\end{itemize}
		\end{itemize} 
	} 
	\cvitem{2020--2021}{
		\textbf{Hiring Committee Member} for tenure-track candidate of University of Florida College of Education. 
	}
	\cvitem{2017--2021}{
		\textbf{Committee Member} at University of Florida Department of Mathematics for standing committees:
		\begin{itemize}
			\item Teaching Methods (\textit{Chair 2019--2021});
			\item Online Course Development; 
			\item Teaching Assistant Training; and
			\item Undergraduate Committee Lower Division.
		\end{itemize}
	} 
	
	%\section{Community Service}
	%	\cventry{2019}
	%		{Julia Robinson Mathematics Festival}
	%		{}
	%		{University of Florida}
	%		{}
	%		{Department representative for K-12 students to explore mathematics through collaborative, creative problem-solving.}
	
	%	\cventry{2015--2017}
	%		{Atlanta Science Festival}
	%		{}
	%		{Georgia State University}
	%		{}
	%		{Department representative in public celebration of local science and technology.}
	
	\section{Professional Affiliations}
	\cvitem{2023--present}
	{\textbf{Tech in Math Ed (TiME) Organizer} for the special topic research group of SIGMAA on RUME.}
	\cvitem{2015--present}
	{\textbf{SIGMAA on RUME}: Special Interest Group of the Mathematical Association of America on Research in Undergraduate Education}
	\cvitem{2015--present}
	{\textbf{MAA}: Mathematical Association of America} 
	%\cvitem{2016--2018}
	%{\textbf{Proof Research Group} of SIGMAA on RUME}
	
	\section{Awards and Fellowships}
	\cvitem{Aug 2024}{
		\textbf{Recognition Award}, from ERAU-WW College of Arts and Sciences for dedicated service, hard work, and leadership during time as Acting Chair for the Department of Mathematics, Science, and Technology.
	}
	\cventry{Apr 2023}
	{Monetary Award}
	{}
	{2022-2023 Faculty 'Superstar' Champion badge from ERAU-WW COAS Dean and Chancellor.}
	{}{}
	\cventry{Apr 2023}
	{Recognition Award}
	{}
	{2022-2023 ERAU-WW COAS Faculty Council Collegiality nominee.}
	{}{}
	\cventry{2022--2023}
	{Fellowship}
	{}
	{Mathematical Association of America Project NExT. Red22 cohort.}
	{}{}
	\section{Travel Grants}
	\cventry{2025}
	{Internal}
	{}
	{from ERAU-WW Faculty Development Research Program for Conference on Research in Undergraduate Mathematics Education, February 27 - March 1.}
	{}{}
	\cventry{2024}
	{External}
	{}
	{from WestEd for Workshop on Future Directions for Mathematics Education Research, Policy, and Practice, April 17-19.}
	{}{}
	\cventry{2023}
	{External}
	{}
	{from Institute for Mathematics and its Applications University of Minnesota for Workshop on Developing Online Learning Experiments Using Doenet, May 22-26.}
	{}{}
	\cventry{2023}
	{Internal}
	{}
	{from ERAU-WW Faculty Development Research Program for Conference on Research in Undergraduate Mathematics Education, February 23-25.}
	{}{}
	\cventry{2022}
	{Internal}
	{}
	{from ERAU-WW Faculty Development Research Program for Joint Mathematics Meeting 2022, January 5-8.}
	{}{}
	\cventry{2021}
	{Internal}
	{}
	{from UF Center for Applied Mathematics for Joint Mathematics Meeting 2021, January 6-9}
	{}{}
	\cventry{2020}
	{Internal}
	{}
	{from UF College of Liberal Arts and Sciences for Joint Mathematics Meeting 2020, January 15-18.}
	{}{}
	\cventry{2017}
	{External}
	{}
	{from the American Mathematical Society for the AMS Spring 2017 Southeastern Sectional Meeting, March 10-12.}
	{}{}
	
	%	\cventry{2016}
	%		{Travel Grant}
	%		{}
	%		{from the AMS Graduate Student Chapter at Georgia State University for the AMS Spring 2016 Southeastern Sectional Meeting, March 5-6}
	%		{}{}
	
	%	\cventry{2015}
	%		{Recognition Award}
	%		{}
	%		{from the Georgia State University Department of Mathematics and Statistics as the 2015 Graduate Teaching Assistant of the Year}
	%		{}{}
	
	%	\cventry{2015}
	%		{Recognition Award}
	%		{}
	%		{from Georgia State University as a 2015-2016 Who's Who Among Students in American Universities \& Colleges}
	%		{}{}
	
	%	\cventry{2015}
	%		{Travel Grant}
	%		{}
	%		{from the American Mathematical Society Graduate Student Chapter at Georgia State University for the American Mathematical Society Spring Southeastern Regional Conference, March 27-29}
	%		{}{}
	
	\section{Notable Coursework}
	\cvitem{\textbf{Mathematics}}
	{\textbf{33 Graduate-Level Credit Hours}: Advanced Matrix Analysis I \& II, Abstract Algebra I \& II, Real Analysis I \& II,  Partial Differential Equations, Special Topics in Mathematics I \& II (Topology, Graph Theory), Directed Research (Graph Theory), Mathematical Biology. \textit{Qualifying Exams in Matrix Analysis and Abstract Algebra.} }
	
	\cvitem{\textbf{Mathematics Education}}
	{\textbf{15 Graduate-Level Credit Hours}: Teaching College Mathematics, Qualitative Research in Education I \& II, Epistemology of Advanced Mathematical Concepts, Learning Theories in Collegiate Mathematics Education. \textit{Qualifying Exam in Collegiate Mathematics Education.} }
	
	\cvitem{\textbf{Statistics}}
	{\textbf{6 Graduate-Level Credit Hours}: Mathematical Statistics, Linear Statistical Analysis.}
	
	\cvitem{\textbf{Data Science}}
	{\textbf{5 Coursera Courses}: Introduction to Data Science in Python, Applied Plotting, Charting \& Data Representation in Python, Applied Machine Learning in Python, Applied Text Mining in Python, Applied Social Network Analysis in Python.}
	
\end{document}